Examples of Customization

### 2016-08-23 custom_examples.Rmd
Attempt to fix sim_outcome, problem with unused arguments
Add example custom functions, all options working for sim_outcome

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  1 + y * sin(2 * pi * (day / 365))
}
calc_t(n = 5, y = .3, trend = "custom", custom_func = sintrend)
plot(calc_t(1000, y = .3, trend = "custom", custom_func = sintrend))
```

@@

>>>>

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  base <- 1 + y * sin(2 * pi * (day / 365))
  rnorm(n, mean = base, sd = 1)
}
calc_t(n = 5, y = .3, trend = "custom", custom_func = sintrend)
plot(calc_t(1000, y = 2, trend = "custom", custom_func = sintrend))
```

@@

##Custom functions for outcome

```{r}
#For baseline:
custombase <- function(n, slope, intercept){
  day <- c(1:n)
  baseline <- day*slope + intercept
  return(baseline)
}

#Example
custombase(n=5, slope = .3, intercept = 55)

#For lambda:
customlambda <- function(exposure, rr, constant, baseline){
  log_lambda <- log(baseline) + log(rr) * exposure + constant
  lambda <- exp(log_lambda)
  return(lambda)
}

#Example:
testlambda <- customlambda(testexp$x, testbase$baseline, rr=1.01, constant = 4)
```
